API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex
COSMIT Fixed my name

\author{Lars~Buitinck~\inst{1} \and
        Gilles~Louppe~\inst{2} \and
        Mathieu~Blondel~\inst{3} \and
        Fabian~Pedregosa~\inst{4} \and
        Andreas~Mueller~\inst{5} \and
        Olivier~Grisel~\inst{6} \and
        Vlad~Niculae~\inst{7} \and
        Peter~Prettenhofer~\inst{8} \and
        Alexandre~Gramfort~\inst{4,9} \and
        Jaques~Grobler~\inst{4} \and
        Robert~Layton~\inst{10} \and
        Jake~Vanderplas~\inst{11} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{12} \and
        Gaël~Varoquaux~\inst{4}}

>>>>

\author{Lars~Buitinck~\inst{1} \and
        Gilles~Louppe~\inst{2} \and
        Mathieu~Blondel~\inst{3} \and
        Fabian~Pedregosa~\inst{4} \and
        Andreas~C.~M\"uller~\inst{5} \and
        Olivier~Grisel~\inst{6} \and
        Vlad~Niculae~\inst{7} \and
        Peter~Prettenhofer~\inst{8} \and
        Alexandre~Gramfort~\inst{4,9} \and
        Jaques~Grobler~\inst{4} \and
        Robert~Layton~\inst{10} \and
        Jake~Vanderplas~\inst{11} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{12} \and
        Gaël~Varoquaux~\inst{4}}
